babette: BEAUti 2, BEAST2 and Tracer for R

### 2018-02-15 article.tex
better keyword
Before implementing feedback GL

% Ideal
%\begin{keywords}
%  computational biology, evolution, phylogeny, BEAST2, R
%\end{keywords}

% Dirty hack
{\bf Keywords:} computational biology, evolution, phylogeny, BEAST2, R

@@

\verb;babette;'s development takes place on GitHub \cite{github},
\url{https://github.com/richelbilderbeek/babette}, 
which accommodates collaboration \cite{perez2016ten} 
and improves transparency \cite{gorgolewski2016practical}.
\verb;babette;'s GitHub facilitates feature requests and has a guidelines how to do so.

>>>>

% Ideal
%\begin{keywords}
%  computational biology, evolution, phylogenetics, BEAST2, R
%\end{keywords}

% Dirty hack
{\bf Keywords:} computational biology, evolution, phylogenetics, BEAST2, R

@@

\verb;babette;'s development takes place on GitHub \cite{github},
\url{https://github.com/richelbilderbeek/babette}, 
which accommodates collaboration \cite{perez2016ten} 
and improves transparency \cite{gorgolewski2016practical}.
\verb;babette;'s GitHub facilitates feature requests and has guidelines how to do so.
